\section*{\xiaoerhao \Rom Abstract}
\xiaosihao
\Rom
Android System has been widely used as an embedded operating system recently. It owns powerful calculating ability, abundant I/Os and it is quite easy to develop on it. Meanwhile, electrocardiogram(ECG) monitoring devices are changing its way to mobility and smart. Therefore, the combination of them has become the main aim of most of the related studies. Many Android-based ECG monitoring system have been performed and also, there are some researches aiming at the specific ECG waveform analyzing algorithms. The ultimate goal of these researches is to build a mini-type ECG monitor as well as an online warning system based on Android's powerful calculation and easy access to the Internet. However due to the limited size of most of Android devices and other facts, these designs hardly could display the ECG waveform effectively, which means that the health care workers are not able to fetch what they expected before. 

In this study, a new type of Android ECG monitoring application has been developed. It exhibits the ECG waveform with high level of effectiveness, with the Bluetooth connection to a ECG sensor. Below are its four main features: (1) its effective display method based on portrait and landscape layout switching; (2) a user interface to measure the waveform; (3) SQLite-based ECG database which is easy to manage and (4) an accurate, robust R-peak detecting algorithm. The application has passed a series of tests with a stable and normal performance. Tests shown that the Sensitivity of the R-peak detecting algorithm is 99.7\% and the Accuracy of it is 99.7\%, too. The application can be a success in monitoring ECG signals. 


\noindent
\textbf{\sihao Key Words}:
Android Application; Electrocardiogram; R-peak detection
\indent 